On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate

### 2016-07-25 Main.Rmd
引用スタイルなども追加。3209 words

---
title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
# csl: new-phytologist.csl
output:
    html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: true
    pandoc_args: [
      "--latexmathml"
    ]
# word_document:
#   toc: true
#   fig_caption: true
#   pandoc_args: [
#   "--latexmathml"
#   ]
---

@@

if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")

base_size_default <- 12
R_abs_W <- .79
FR_abs_W <- .262
R_abs_WFR <- .783
FR_abs_WFR <- .20
# R_abs_W <- .93
# FR_abs_W <- .311
# R_abs_WFR <- .922
# FR_abs_WFR <- .267

options(warn = -1)
source("~/Dropbox/Publish/2016R_Fr/Functions_CurveFit.R")
source("~/Dropbox/Publish/2016R_Fr/Pg_Estimate.R")
source("~/Dropbox/Publish/2016PgEstimate/PgAnalyze.R")
source("~/Dropbox/Publish/2016PgEstimate/YieldAnalyze.R")
source("~/Dropbox/Publish/2016PgEstimate/Captions.R")
options(warn = 1)
} else {
library(knitr)
}

opts_chunk$set(echo = FALSE, fig.width = 7.5, fig.height = 7.5, out.width = "100%",
           message = FALSE, warning = FALSE, cache = F, eval = T)
```

@@

X_div <- 100
X_range <- seq(0, 1, length.out = X_div)

InteractionDat <-
  data_frame(X = rep(X_range, times = 2),
           ETR = c(dbeta(X_range, 3, 4.5) * 1.2, dbeta(X_range, 4.5, 3)),
           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))

@@

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, group = Trtm)) +
  theme_bw2() +
  geom_line() +
  scale_linetype_manual(values = c(2, 1)) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
  xlab("PSI-biased level of measuring light") +
  ylab("Relative electron transport rate") +
  gg_xy(c(.1, .9, 0, 3))

CapInteract <-
  "Fig. 2  Conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves; solid line) and PSI-light (PSI-leaves; dashed line) in response to the PSII/PSI-light level of measuring light. PSII-leaves performs a higher ETR under PSII-light and a lower ETR under PSI-light compared to PSI-leaves."
```

```{r Spectra, eval = evalFig}

# set integrate ranges
PFD_integrate_min <- 350
PFD_integrate_max <- 750

IntegratePFD <- 100

panel_names <- c("HIDs and fluorescent lamp", "LEDs", "Sunlight")

# HID_raw <-
#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
# 
# HIDs <-
#   HID_raw %>%
#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
#   select(1, HPS_ = 12, MH_ = 21)
FL_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
  na.omit

FL_Ocean_PFD <-
  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

FL_Ocean <-
  FL_Ocean_raw %>%
  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")

HPS_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

HPS_Ocean_PFD <-
  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

HPS_Ocean <-
  HPS_Ocean_raw %>%
  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")

MH_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

MH_Ocean_PFD <-
  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

MH_Ocean <-
  MH_Ocean_raw %>%
  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")

OceanSPDs <-
  bind_rows(FL_Ocean, HPS_Ocean, MH_Ocean) %>%
  mutate(panel = panel_names[1])

Absorptances <-
  fread("~/Dropbox/materials/SpectrumCucumber.csv") %>%
  filter(Trtm %in% c("W", "WFR", "FL")) %>%
  mutate(wavelength = as.numeric(wavelength)) %>%
  filter(variable == "absorption", Trtm == "W")

Sun <-
  fread("~/Dropbox/materials/Sunlight_JIS.csv") %>%
  setnames(c("wavelength", "Sunlight")) %>%
  left_join(., Absorptances, by = "wavelength") %>%
  transmute(wavelength, Sun = Sunlight, Shade = Sunlight * (100 - ave), Absorptance = ave)

# Sun: JIS C8904-3

LEDs <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, W, FR, B = B_HL, R = R_SR) %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[2]) %>%
  na.omit

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
             value = c(2.1, .7, 3, 4, 4.4, 3.8, 1.2, 0.3, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             panel = rep(panel_names,  c(3, 4, 2)))

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2() +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey80", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  facet_wrap( ~ panel, ncol = 1) +
  gg_xy(c(380, 820, 0, 5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

CapSPD <-
  "Fig. 3  Spectral photon flux density distribution of light. The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
```

@@

**Abbreviations**
Chl: chlorophyll
ETR: Electron transport rate
FR: far-red
LED: light-emitting diode
*P*~n~: Net photosynthetic rate
PPFD: photosynthetic photon flux density
PSI: photosystem II
PSII: photosystem I
SPD: spectral PFD distribution

@@

  The photosynthetic rate is one of the most important and fundamental phenotype in the plant sciences.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
  The measured rates are also used for the estimation of the other photosynthetic parameters, such as initial slope of light response of *P*~n~ and the maximum photosynthetic rate [e.g. @Sharkey_et_al2007PCE].
  Based on the measured rate and estimated parameters, the effectiveness of the treatment is discussed in agricultural and horticultural studies.
  Therefore, the accurate and reliable measurements of the photosynthetic rate must be essential.

  A number of studies have reported that the SPD of light used for the measurement (i.e. measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under an identical SPD of measuring light irrespective of leaf growth conditions in agricultural and horticultural studies.
  The most widely-used measuring light might be mixture of blue + red LED light **(BRlight)** provided by light sources installed in commercial photosynthesis analyzing systems.
  The use of the artificial light sources might enable better control of the incident photosynthetic photon flux density (PPFD) and thereby might certificate the reproducibity of the experiments.

  @Walters2005JXB warned that the measurement with a different SPD of light from **grothw light**, do not necessarily reflect the functioning of the photosynthesis under growth conditions.
  Our recent paper, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  @Murakami_et_al2016PP grew cucumber seedlings under white LED light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently compared their *P*~n~ under blue + red LED light and the sunlight-like SPD of light.
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under blue + red LED light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight.
  **Based on the results obtained from the measurement under blue + red LED light, WFR-leaves are evaluated to be less lively and low quality, despite the comparable potential under the sunlight.**
  In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~ (唐突感ある).
  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.

  In this short article, we introduce several articles reporting the interaction and the likely causes---the distribution of the excitation energy between the photosystems.
  Subsequently we suggest the situations where the interaction should be cared.
  **We also discuss the practical methods for the *P*~n~ measurements 光質に関した的なフレーズ, and related future works.**
  It is known that the SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photo**inhibition** [@Zavafer_et_al2015JPP] and light penetrating depth within the leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited review articles on these topics are available.

# How the interactions are generated

  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The electron transports are powered by excitation energy, which is derived from absorbed photons.
  **The excitation energy transferred to the reactino centers of PSII and PSI drives photochemical reactions **
  **Note that the term "energy" is used in **
  **The two photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).**
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
  When PSII absorbs excess excitation energy **under the imbalanced SPD of light**, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII is lowered **詰まり由来で的フレーズ** (Fig. 1A).
  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
  In both cases, the excesss energy is dissipated as heat and fluorescence (ROS生成とダメージの話をするか...), and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  <!-- **おまけ部分** -->
  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~). -->
  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
  <!-- Gentyに触れるか？AEF -->

  The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？).
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
  On contrary, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the EED is a determinant of the distribution under a given SPD of light.
  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
  A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).

  Apparently, the EED is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
  The stoichiometry is reported to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
  The adjustments in the EED properties might help the leaves to keep the higher photosynthetic light use efficiency under growth light.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  A slight imbalance in the EED might be covered up by the state transitions.
  The adjustments in the distribution properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Walters_Horton1995aPlanta showed the interaction in the O~2~ evolution yield using halogen lamp and color-conversion filter.
  @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
  **They demonstrated that the interaction can occur 違う組合せでも**.
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.

@@

# Where the interaction should be cared.

  This interaction **has** considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ sturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
  In such conditions, the biases in the ETR should be directly reflected in the *P*~n~.
  Therefore, the *P*~n~ at light-limited conditions may be measured with particular attentions on the interaction.
  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction. -->

  The mechanisms of the SPD acclimation of **energy distribution** are not yet fully elucidated [see @Murakami_et_al2016PP].
  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
  <!--' Chow and coworkers also reported  -->
  Considering the sensitively adjusted photosystem stoichiometry to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to **possess** different excitation energy distribution properties.

>>>>

---
title: "On the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate"
author: "Keach Murakami, Ryo Matsuda, Kazuhiro Fujiwara"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
csl: ECB.csl
output:
    html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: F
    fig_caption: true
    pandoc_args: [
      "--latexmathml"
    ]
# word_document:
#   toc: true
#   fig_caption: true
#   pandoc_args: [
#   "--latexmathml"
#   ]
---

@@

if(evalFig){
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup.R")
} else {
library(knitr)
}

opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5, out.width = '500pixel', out.heit = '500pixel', dpi = 200, fig.align = "center", message = FALSE, warning = FALSE, cache = F, eval = T)
```

```{r Captions}
CapETRs <-
  "Fig. 1  The conceptual diagrams of the effects of the excitation energy distribution between the photosystems (PSII and PSI) on the photosynthetic electron transport rate (ETR). Electron flow (grey lines) and energy flow (black lines) of leaves grown under PSII-light (A, B) and PSI-light (C, D) measured using PSII-light (A, C) and PSI-light (B, D) were shown."

CapInteract <-
  "Fig. 2  The conceptual diagram of the photosynthetic electron transport rates (ETR) of leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-light level of measuring light."
```

@@

X_div <- 101
X_range <- seq(0, 1, length.out = X_div)
x_breaks <- c(0.2, 0.4, 0.65)

InteractionDat <-
  data_frame(X = rep(X_range, times = 2),
           ETR = c(sqrt(dbeta(X_range, 4.5, 3)) * 1.1, sqrt(dbeta(X_range, 3, 4.5))),
           Trtm = rep(c("PSII-leaves", "PSI-leaves"), each = X_div))

@@

InteractionPoint <-
  InteractionDat %>%
  filter(X %in% x_breaks)

InteractionText <-
  InteractionDat %>%
  filter(X %in% x_breaks) %>%
  mutate(labels = c("far-red LED light", "Sunlight", "blue + red LED light", rep("", length(x_breaks)))) %>%
  mutate(ETR = c(0.1, 0.1, 0.1, numeric(length(x_breaks))))

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
  theme_bw2() +
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = element_blank()) +
  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
  geom_line() +
  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
  scale_fill_manual(values = c("white", "black")) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_continuous(breaks = c(0.1, 0.9), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
  xlab("PSII-biased level of measuring light") +
  ylab("Relative electron transport rate") +
  gg_y(c(0, 2))
```

@@

**Abbreviations**
BR-light: blue + red LED light 
Chl: chlorophyll,
ETR: electron transport rate,
FR: far-red,
LED: light-emitting diode,
*P*~n~: net photosynthetic rate,
PFD: photon flux density,
PPFD: photosynthetic photon flux density,
PSI: photosystem I,
PSII: photosystem II,
SPD: relative spectral PFD distribution

@@

  The photosynthetic rate is one of the most important and fundamental phenotype in the plant sciences.
  The rates are measured, evaluated, and compared among the leaves cultivated under different conditions, typically the control and treatment.
  The measured rates are also used for the calculation of the other photosynthetic parameters, such as light, water, and nitrogen use efficiencies.
  The effectiveness of treatments is sometimes discussed based on the measured photosynthetic rate and calculated parameters in agricultural and horticultural studies.
  Therefore, the accurate measurements of the photosynthetic rate must be essential.
  A number of studies have reported that the relative spectral photon-flux-density (PFD) distribution (SPD) of light used for the measurement (i.e. measuring light or actinic light) affected the net photosynthetic rates (*P*~n~) of leaves [e.g. @McCree1972AM; @Inada1976PCP].
  To eliminate this direct effect from the comparison, *P*~n~ is usually measured under a single-level SPD of measuring light irrespective of the leaf growth conditions in these fields.
  The most widely-used measuring light might be mixture of blue + red LED light (BR-light) provided by light sources installed in commercial photosynthesis analyzing systems.
  The use of the artificial light sources might enable precise control of the photosynthetic PFD (PPFD) and SPD incident on the leaf thereby ensure the reproducibility and reliability of the experiments.

  @Walters2005JXB pointed out that the measurements with a SPD of light different from growth light do not necessarily reflect the functioning of the photosynthesis under growth conditions.
  Our recent study, indeed, experimentally demonstrated this problem in the *P*~n~ measurements [@Murakami_et_al2016PP].
  In that experiment, cucumber seedlings were grown under white light-emitting diode (LED) light without and with supplemental far-red (FR) LED light (W and WFR), and subsequently the *P*~n~ of the leaves were compared under BR-light and a sunlight-like SPD of light.
  The *P*~n~ of W-leaves was greater than that of WFR-leaves under BR-light, while the rates were comparable---or slightly greater in the WFR-leaves---under artificial sunlight [@Murakami_et_al2016PP].
  Based on the results obtained from the measurement under BR-light, the prospective growth rate of WFR-plants is evaluated to be smaller than that of W-plants despite the comparable *P*~n~ under the sunlight.
  **In other words, the SPDs of light incident on the leaf during growth and measurement interacted on the *P*~n~**.
  If the plants were evaluated without considering the interactions, the selection and decision might be distorted.

  In this short article, we introduce several articles reporting the interaction and the likely causes---the distribution of the excitation energy between the photosystems.
  Subsequently we suggest the situations where the interaction should be cared.
  We also discuss the good practice for the selection of the SPD of measuring light used for *P*~n~ measurements.
  The SPD of light affects the photosynthesis through the other mechanisms, such as the stomatal response [@Shimazaki_et_al2007AnnRev], photoinhibition [@Zavafer_et_al2015JPP], and the light-penetrating depth within a leaf [@Terashima_et_al2009PCP].
  Although these subjects are not referred in this article, the cited review articles on these topics are available.

# How the interaction is generated

  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The reactions are powered by excitation energy derived from absorbed photons.
  **The excitation energy  the photosystems and their anntena complexes is transferred to the reaction centers, and then consumed photochemical reactions in the unit of mol**
  **Note that the term "energy" is used in **
  **The two photochemical reactions at PSII and PSI enables electron transfer against the redox potential (called the Z scheme).**
  Because the photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) through the thylakoid membrane is limited by the slowest step (Fig. 1).
  When PSII absorbs excess excitation energy under PSII-biased light, the energy distribution to PSI limits the ETR and thus the photochemical quantum yield of PSII should be lowered (Fig. 1A).
  When PSI absorbs excess excitation energy, the energy distribution to PSII limits the ETR and the yield of PSI should be lowered (Fig. 1D).
  In both cases, the excesss energy is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---ETR per absorbed PFD---becomes smaller.
  An imbalance excitation between the photosystems can harm leaves by generating reactive oxygen species, which cause oxidative damage to chloroplast components [for reviews, see @Asada1999AnnRev; @Asada2006PP].
  Balancing the excitation energy distribution (EED) between PSII and PSI is essential for plants to keep the high photosynthetic quantum yield.

  <!-- **おまけ部分** -->
  <!-- Note that the balanced distribution might not be a fifty-fifty. -->
  <!-- Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. Chl fluorescence parameter *F*~v~/*F*~m~). -->
  <!-- Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII. -->
  <!-- Therefore, under the fifty-fifty distribution, the energy supply to PSII is insufficient and that to PSI is excessive. -->
  <!-- A little bit greater distribution to PSII might be required to make maximum use of the absorbed photons. -->
  <!-- Gentyに触れるか？AEF -->

  <!-- The imbalance in the EED between the photosystems is supposed to occur ordinarily (どこで？太陽光？). -->
  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chl absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb the longer wavelengths of light and that PSI contains a greater amount of chl *a* than PSII.
  On contrary, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [@Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the EED is a determinant of the distribution under a given SPD of light.
  In several studies of the SPD acclimation of the photosynthetic apparatus, light with a given SPD is categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI.
  A given SPD of light is classified according to the PFD in the FR waveband in the relative context.
  For instance, a SPD of light, which is evenly absorbed by PSII and PSI in PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AC).
  Thus, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.

  Apparently, the EED is affected by the composition of the thylakoid membrane, especially by the stoichiometry between PSII and PSI.
  The stoichiometry seems to be adjusted to the SPD of growth light.
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases; conversely, under PSI-light, the relative amount increases to achieve a balance [e.g. @Melis1991BBA; @Pfannschmidt_et_al1999Nature].
  The possible involvement of the change in the composition within the respective photosystems in the SPD acclimation was also suggested [@Walters_Horton1995bPlanta; @Murakami_et_al2016PP].
  <!-- Galka_et_al2012PC -->
  The adjustments in the EED properties might help the leaves to keep the higher photosynthetic light use efficiency under growth light.
  In the short term within an hour, an imbalance in the EED is, at least partly, relieved by the reversible allocation of the light-harvesting antenna complex of PSII (LHCII) between PSII and PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].
  Although a slight imbalance in the EED might be covered up by the state transitions, the long-term adjustments in the EED properties are supposed to occur when state transitions are insufficient to counterbalance the uneven EED [@Dietzel_et_al2008FJ].

  The SPD of growth light affects the EED properties of a leaf, which modifies the responses of the ETR and thereafter *P*~n~ to the SPD of measuring light.
  Thus, the SPDs of growth light and measuring light do not only directly affect the *P*~n~ but also indirectly affect it through their interaction.
  The expected interactions have been reported in several studies [@Chow_et_al1990PNAS; @Walters_Horton1995aPlanta; @Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  In their pioneering study on *Pisum sativum*, @Chow_et_al1990PNAS grew plants under cool-white fluorescent lamps with yellow Plexglas (FR-poor PSII-light) and incandescent bulbs with red Plexglas (FR-rich PSI-light) and measured the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---under PSII- and PSI-light.
  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
  A similar trends were observed in *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PP].
  @Walters_Horton1995aPlanta showed the interaction in the O~2~ evolution yield using halogen lamp and color-conversion filter.
  @Hogewoning_et_al2012PC found the interaction in the *P*~n~ using artificial sunlight (PSII-light) and shadelight (PSI-light) as growth light and 19 monochromatic LED light as measuring light.
  They demonstrated that the interaction can occur 違う組合せでも**.
  @Murakami_et_al2016PP showed the interaction in the *P*~n~ using white LED light without or with FR LED light (PSII-light and PSI-light) as growth light and BR-light (PSII-light) and artificial sunlight (PSI-light) as measuring light.
  The potential problem in the use of BR-light for the *P*~n~ measurements was clearly demonstrated.

@@

# Where the interaction should be cared

  This interaction may have considerable impact on the *P*~n~ especially under the light limited and/or CO~2~ saturated conditions, where the extent of the ETR is dominant factor for the photosynthetic CO~2~ uptake rate [@vonCaemmerer_Farquhar1981Planta].
  In such conditions, any bias in the ETR is directly reflected in the *P*~n~.
  Therefore, the *P*~n~ at light-limited conditions should be measured with particular attentions on the interaction.
  <!-- In contrast, under a higher PFDs and/or CO~2~ limtied conditions, the *P*~n~ is determined by the CO~2~ fixation process in the Calvin cycle rather than the ETR. -->
  <!-- In such conditions, the effects of the biases in the ETR on *P*~n~ may be demagnified. -->
  <!-- In our experiment, however, the interaction was observed under a high PFD (1200 µmol m^--2^ s^--1^) and a low CO~2~ concentration condition (20 Pa in the intercellular space) [@Murakami_et_al2016PP], suggesting the other factor involved in the interaction. -->

  The mechanisms of the SPD acclimation of the EED property are not yet fully elucidated [see @Murakami_et_al2016PP].
  <!--' @Walters_Horton1995aPlanta confirmed a typical adjustment in the photosystem stoichiometry in response to the slight difference in the SPD of growth light. -->
  <!--' They also found no difference in the stoichiometry between the leaves grown with and without supplemental FR [@Walters_Horton1995bPlanta]. -->
  <!--' Chow and coworkers also reported  -->
  Considering the sensitively adjusted photosystem stoichiometry in response to the SPD of light [@Walters_Horton1995aPlanta], the interaction may be always taken into account whenever the *P*~n~ and related parameters are evaluated.
  The impacts of the interaction on the photosynthetic rates should be payed particular attention when the measured leaves are expected to represent different EED properties.
